Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-09-08 draft/draft0.tex
updates

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
   and obtains wrong results (the red solid lines).
   %The red solid lines show their positions and shapes when the wrong cosmologies 
   % are assumed to compute distance from measured redshift.
   %The misestimation of angular diameter distance lead to wrong 
   Right panel shows the misestimation of angular diameter distance when the wrong cosmologies are adopted.
   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the scaling effect in wrongly assumed cosmologies.
A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.

Suppose that we are probing the shape of some objects in the Universe.
We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute its sizes in the radial and transverse directions from the relations of 
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter, $D_A$ is the angular diameter distance.
In the particular case of a flat universe with constant dark energy EoS, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
This paper we focus on the misestimation of $\Delta r_{\bot}$,%scaling of angular size,
which can be described by the following quantities
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\bot} \equiv \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.

The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
using redshift-distance relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5, \nonumber \noindent
\end{eqnarray}
the shapes of the squares appear distorted (AP effect),
and their volumes are changed (volume effect).
In the cosmological models in model (i,iii) we see a compression of size (in both angular and LOS direction)
and the degree of compression increases with increasing distance,
while in models (ii,iv) we see stretch of size whose degree also evolves with redshift.
Thus, when wrong cosmological parameters are adopted,
the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.

In this paper we will use the galaxy angular 2pCF to probe the redshift dependence of the distortion in angular direction.
In the right panel of Figure \ref{fig_xyquan} we plot the redshift dependence of the change in angular size, 
${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, in the four wrong cosmologies.
In all cosmologies, there is clear evolution of ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ 
in the redshift range $0<z<2$.
E.g., when use the quintessence cosmology 
$\Omega_m=0.26,\ w=-0.5$ to infer the postions of objects,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

We test the method on the Horizon Run 4  (HR4) simulation \citep{hr4}.
HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
It adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}.
The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

@@

The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the wrongly assumed cosmological parameters.

>>>>

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
   and obtains wrong results (the red solid lines).
   %The red solid lines show their positions and shapes when the wrong cosmologies 
   % are assumed to compute distance from measured redshift.
   %The mis-estimation of angular diameter distance lead to wrong 
   Right panel shows the mis-estimation of angular diameter distance when the wrong cosmologies are adopted.
   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the scaling effect caused by wrongly assumed cosmological parameters.
A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.

Suppose that we are probing the size of some objects in the Universe.
We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute its sizes in the radial and transverse directions using the following formulas
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter and $D_A$ is the angular diameter distance.
In the particular case of a flat universe composed by a cold dark matter component and a constant EoS dark energy component, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case wrong values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in wrong estimation in the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been investigated in \cite{Li2014,Li2015,Li2016}.

In this paper we focus on the mis-estimation of the angular size $\Delta r_{\bot}$. %scaling of angular size,
The ratio of mis-estimation is
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\bot} \equiv \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmologies, respectively.

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at various distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5, \nonumber \noindent
\end{eqnarray}
as a result, 
the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;

The mis-estimation of angular size, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, 
are displayed in the right panel of Figure \ref{fig_xyquan}.
All cosmologies, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

%Thus, when wrong cosmological parameters are adopted,
%the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.

In sum, as a consequence of incorrectly adopted cosmologies, 
the size of the objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$.

@@

We test the idea on the mock galaxy samples provided by the Horizon Run 4  (HR4) N-body simulation \citep{hr4}.
(Check Cris's revision on BOSS AP paper!!!!)
HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
It adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}.
The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

@@

The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the cosmological effect.
